Analysis of the time-dependent response to Estradiol through ChIP-Seq data

### 2018-11-26 Manuscript_Figures_Combined.Rmd
Add Suppl. Figure 92
Added mRNA data
code working for markdown

```{r ER qRPCR, child = 'qPCR_ER/Manuscript_Figures.Rmd'}
```

@@

```{r ER ChIP-seq, child = 'ChIP-seq_ER/rmarkdown.Rmd'}
```

@@

```{r ER qRIME, child = 'qPLEX-RIME_ER/02.Supplementary.Rmd'}
```

@@

```{r GRHL2 Chip, child = 'ChIP-seq_GRHL2/Manuscript_Figures.Rmd'}
```

```{r GRHL2 qRIME, child = 'qPLEX-RIME_GRHL2/rRunTMTanalysis.Rmd'}
```

#GRHL2 qPLEX-RIME Analysis
```{r GRHL2 eRNA, child = 'eRNA/plot_eRNA.Rmd'}
```

>>>>

```{r ER qRPCR, child = 'S1_qPCR_ER/Manuscript_Figures.Rmd'}
```

@@

```{r ER ChIP-seq, child = 'S2_ChIP-seq_ER/rmarkdown.Rmd'}
```

@@

```{r ER qRIME, child = 'S3_qPLEX-RIME_ER/02.Supplementary.Rmd'} 
```

<!-- ```{r GRHL2 qRIME, child = 'qPLEX-RIME_GRHL2/rRunTMTanalysis.Rmd'} -->
<!-- ``` -->

@@

```{r GRHL2 Chip, child = 'S5_ChIP-seq_GRHL2/Manuscript_Figures.Rmd'}
```

#Effect of GRHL2 expression on eRNA and mRNA 
```{r GRHL2 eRNA, child = 'S6_eRNA/plot_eRNA.Rmd'}
```

#Effect of GRHL2 expression on H3K27ac

<!-- ```{r GRHL2 H3K27ac, child = 'S7_ChIP-seq_H3K27ac_siGRHL2/plot_eRNA.Rmd'} -->
<!-- ``` -->

### 2018-11-26 S2_ChIP-seq_ER/rmarkdown.Rmd
code working for markdown

# Technical Session Info
The following code describes the R environment used to generate this document and will help making it fully reproducible should there be future updates in any of the packages.
```{r sessionInfo}
sessionInfo()
```

>>>>

<!-- # Technical Session Info -->
<!-- The following code describes the R environment used to generate this document and will help making it fully reproducible should there be future updates in any of the packages. -->
<!-- ```{r sessionInfo} -->
<!-- sessionInfo() -->
<!-- ``` -->
